Title Goes Here

### 2020-03-26 analysis/paper/paper.Rmd
distance btw y axis

@@

>>>>

# distance between two y axis 
vertical_dist = function(landmarks, pt1, pt2) {
  d = abs(landmarks$Y[pt1] - landmarks$Y[pt2])
  d * as.numeric(levels(landmarks$SCALE))
}

# Tang length of sp: TL, distance between landmark 10-7 or 3-7, (y axis)
tl_dist <- function(landmarks) {
  t1 = vertical_dist(landmarks, 10, 7)
  t2 = vertical_dist(landmarks, 3, 7)
  max(t1, t2)
}

TL <- tl_dist

# Maximum length of stem:

@@

```{r}
# artifacts from SYG6 site

```
